### 2014-06-09 ijlyttle/first_pass.Rmd
gets as far as generating Gini coefficients

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggvis)
```

@@

>>>>

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(reshape2)
library(lubridate)
library(ggvis)
```

@@

One of the tracks to investigate is inequality. I see there is a package, `ineq` on CRAN, that claims to have a Gini-coefficient function, so that seems like a good place to start.

```{r ineq}
library(ineq)
```

Let's get an idea, for each country and subject, an estimate of the inequality of outcomes.

NOTE: `dplyr` seems to choke on grouping of data.frames with NA, hence the `filter()`.

Also: is there a problem the help text for `dplyr::grouped_df`? The description of `drop` seems backwards to me.

```{r twiddle}
df_twiddle <- student2012 %>%
  select(country = CNT, age = ST06Q01,
         math = PV1MATH, reading = PV1READ, science = PV1SCIE) %>%
  melt(id.vars = c("country", "age"), 
       variable.name = "subject", 
       value.name = "score")  %>%
  do(filter(., complete.cases(.))) %>%
  dplyr::group_by(country, subject) %>%
  summarize(n = n(), gini_coeff = ineq(score, type="Gini")) %>%
  arrange(as.character(country))
```
